\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{url}
\begin{document}
\begin{center}
\thispagestyle{empty}
\huge \textbf{Jiachen (Amber) Liu \\}
\normalsize amberljc@umich.edu $\mid$ (734) 881 4120 $\mid$
\url{http://www-personal.umich.edu/~amberljc/}
 \\
\hrulefill
\end{center}
\linespread{1.5}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\large \textbf{University of Michigan (U of M)} \hfill \normalsize Ann Arbor, MI \\
\textit{Ph.D.Candidate in Computer Science; Advised by Prof. Mosharaf Chowdhury}  \hfill Aug 2020 - Apr 2025 \\
\vspace{-1em}
\begin{itemize}
\vspace{-0.8em}
% \item Advisor:  Prof. Mosharaf Chowdhury
% \vspace{-0.8em}
% \item GPA:3.95/4.00
\vspace{-0.8em}
\item \textbf{Honors:} Ph.D. Student Fellowship (U of M). ML and Systems Rising Stars (Program of 2023)
\vspace{-0.8em}

\end{itemize}
\textit{B.S.E. in Data Science, Minor in Mathematics}  \hfill Sep 2018 - May 2020 
\begin{itemize} 
\vspace{-0.8em}
  \item \textbf{Honors:} Dean's List (2018), Dean's List (2019), 2019 University Honors 
\end{itemize}
\vspace{-0.7em}
\large \textbf{Shanghai Jiao Tong University (SJTU)} \hfill \normalsize Shanghai, China \\
\vspace{-0.3em}
\textit{B.S. in Electrical Computer Engineering} \hfill \hfill Sep 2016 - Aug 2020 
\begin{itemize}
\vspace{-0.6em}
  \item \textbf{Honors:} Shanghai Outstanding Graduate (Top 5\%), Dean’s List (Top 5\%), Undergraduate Scholarship (Top 10\%) % Champion of Shanghai University Women's Basketball Association League  (2017),  Distinguished Academic Achievement Award, 
\vspace{-0.6em}
\end{itemize}
\large \textbf{Massachusetts Institute of Technology} \hfill  \normalsize Cambridge, MA \\
\textit{Visiting researcher at EECS CSAIL, Advised by Prof. Samuel Madden}  \hfill May 2019 - Jan 2020



\noindent \textbf{\underline{PUBLICATION}} \\
\vspace{-2.8em}
(* = equal contribution) \\
% \begin{enumerate}[itemsep=-6pt, before=\vspace{-\baselineskip}, after=\vspace{-\baselineskip}]
\begin{enumerate}[itemsep=-7pt]

\item Sci-Reasoning: A Dataset Decoding AI Innovation Patterns. \underline{Arxiv 2026.}\\
\textbf{Jiachen Liu*}, Maestro Harmon*, Zechen Zhang.

\item User-Centric Machine Learning Systems. \underline{PhD Dissertation 2025.}\\
\textbf{Jiachen Liu}



\item EXP-Bench: Can AI Conduct AI Research Experiments? \underline{Arxiv 2025.}\\
Patrick Kon*, \textbf{Jiachen Liu*}, Xinyi Zhu, Qiuyi Ding, Jingjia Peng, Jiarong Xing, Yibo Huang, Yiming Qiu, Jayanth Srinivasa, Myungjin Lee, Mosharaf Chowdhury, Matei Zaharia, Ang Chen.


\item Curie: Toward Rigorous and Automated Scientific Experimentation with AI Agents. \underline{Arxiv 2025.}\\
Patrick Kon*, \textbf{Jiachen Liu*}, Qiuyi Ding, Yiming Qiu, Zhenning Yang, Yibo Huang, Jayanth Srinivasa, Myungjin Lee, Mosharaf Chowdhury, Ang Chen.

\item Andes: Defining and Enhancing Quality-of-Experience in LLM-Based Text Streaming Services. \underline{Arxiv 2024.} \\
\textbf{Jiachen Liu}, Zhiyu Wu, Jae-Won Chung, Fan Lai, Myungjin Lee, Mosharaf Chowdhury.

\item Venn: Resource Management Across Federated Learning Jobs.
\underline{MLSys 2025.} \\
\textbf{Jiachen Liu}, Ding Ding, Fan Lai, Yiwen Zhang, Mosharaf Chowdhury.


\item 
Fluid: A Generic Resource-aware Hyperparameter Tuning Execution Engine.  
\underline{MLSys 2021.}  
\\  \textbf{Jiachen Liu*}, Peifeng Yu*, Mosharaf Chowdhury.

\item The ML.ENERGY Benchmark: Toward Automated Inference Energy Measurement and Optimization.
\underline{NeurIPS 2025.} (Spotlight)\\
Jae-Won Chung, \textbf{Jiachen Liu}, Jeff Ma, Ruofan Wu, Oh Jun Kweon, Yuxuan Xia, Zhiyu Wu, Mosharaf Chowdhury


\item Evaluation Framework for AI Systems in "the Wild".
\underline{Arxiv 2025.}\\
Sarah Jabbour, Trenton Chang, Anindya Das Antar, Joseph Peper, Insu Jang, \textbf{Jiachen Liu}, Jae-Won Chung, Shiqi He, Michael Wellman, Bryan Goodman, Elizabeth Bondi-Kelly, Kevin Samy, Rada Mihalcea, Mosharaf Chowdhury, David Jurgens, Lu Wang


\item IaC-Eval: A code generation benchmark for Infrastructure-as-Code programs. In \underline{NeurIPS 2024.} \\
Patrick Kon, \textbf{Jiachen Liu}, Yiming Qiu, Weijun Fan, Ting He, Lei Lin, Haoran Zhang, Owen M. Park, George Sajan Elengikal, Yuxin Kang, Ang Chen, Mosharaf Chowdhury, Myungjin Lee, Xinyu Wang.

\item 
FedTrans: Efficient Federated Learning for Heterogeneous Clients via Model Transformation. In \underline{MLSys 2024.} \\
Yuxuan Zhu, \textbf{Jiachen Liu}, Fan Lai, Mosharaf Chowdhury.

\item Efficient Large Language Models: A Survey.
In \underline{TMLR 2024.} \\
Zhongwei Wan, Xin Wang, Che Liu, Samiul Alam, Yu Zheng, \textbf{Jiachen Liu}, Zhongnan Qu, Shen Yan, Yi Zhu, Quanlu Zhang, Mosharaf Chowdhury, Mi Zhang.

\item  
Auxo: Efficient Federated Learning via Scalable Cohort Identification.
In \underline{SoCC 2023.} \\
\textbf{Jiachen Liu}, Fan Lai, Yinwei Dai, Aditya Akella, Harsha Madhyastha, Mosharaf Chowdhury.

\item  
FedScale: Benchmarking Model and System Performance of Federated Learning.
In \underline{ICML 2022.} \\
Fan Lai, Yinwei Dai, Sanjay Singapuram, \textbf{Jiachen Liu}, Xiangfeng Zhu, Harsha Madhyastha, Mosharaf Chowdhury.
\end{enumerate}


 \vspace{-1em}

\noindent \textbf{\underline{WORK EXPERIENCE}} 
% \\
% \noindent 
% \textbf{University of Michigan, Graduate Student Research Assistant}
% \\
% \quad Area: Machine Learning Systems.     \hfill Aug 2020 - Now

\noindent 
\textbf{Meta, Research Scientist}
\\
\quad Area: LLM Pre- \& Post-training Systems.    \hfill Jun 2025 - Now

\noindent 
\textbf{Meta, Research Scientist Intern / Part-time}
\\
\quad Area: Llama Pre-training Systems.    \hfill May 2024 - Dec 2024

\noindent 
\textbf{Apple, PhD Intern}
\\
\quad Area: Private Machine Learning Framework.    \hfill May 2022 - Aug 2022

% \noindent 
% \textbf{Meta, Research Scientist Intern}
% \\
% \quad Area: Large Language Model Training Systems   \hfill May 2024 - Aug 2024



\noindent \textbf{\underline{TEACHING EXPERIENCE}} \\ 
\noindent \textbf{Graduate Student Instructor}, EECS 598 Systems for GenAI  (U of M) \hfill 2024 Winter

\noindent \textbf{Teaching Assistant}, EECS 484 Database Systems (U of M) \hfill 2019 Fall, 2020 Winter, 2020 Summer


% \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
% \item Lead the weekly recitation classes, hold the office hours and design exam problems.
% \end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{COMMUNITY SERVICE}} \\
\noindent \textbf{Computer Science Engineering Graduate Student Organization at U of M }, \textit{DEI Chair}  \hfill May 2023 - Present


\noindent \textbf{Student Union of Joint Institute at SJTU}, \textit{Vice President} \hfill Jun 2017 - Aug 2018 
%\textit{Vice President} \hfill Shanghai, China
% \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
% % \item Coordinated the work of the various departments under Student Union to ensure the division of labor and cooperation.
% %\item Communicated with all departments' directors weekly to ensure reliable operation.
% %\item Founded the debate team and directed the team to prepare for various competition. 
% \end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RESEARCH EXPERIENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{RESEARCH EXPERIENCES}} 
\\
\noindent 
\textbf{Curie: Automated and Rigorous Scientific Experimentation with AI Agents
}\\
\quad \textit{Advisor: Prof. Mosharaf Chowdhury, Porf. Ang Chen} \hfill 2024 - Now
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Curie is the first AI-agent framework designed for automated and rigorous scientific experimentation. Curie helps answer your curiosity through end-to-end experimentation automation, ensuring that every step—from hypothesis formulation to result interpretation—is conducted with precision, reliability, and reproducibility.
\item \url{https://github.com/Just-Curieous/Curie} 
\end{itemize}

\noindent 
\textbf{Large Language Models (LLM) Energy Leaderboard} \\
\quad \textit{Advisor: Prof. Mosharaf Chowdhury} \hfill 2023 - 2024
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Developed an evaluation tool that quantifies the energy consumption of LLMs under different serving scenarios.
\item  Implemented an online interactive system allowing users to compare the generated content and energy efficiency of different LLMs, thereby understanding trade-offs between performance and energy consumption.
\item \url{https://ml.energy/leaderboard/}
% Offered a comprehensive view of how different LLMs compare in terms of energy consumption, aiding in informed decision-making for LLM applications.
\end{itemize}
 
\noindent 
\textbf{FedScale: A Scalable and Extensible Federated Learning (FL) Benchmark}
\\
\quad \textit{Advisor: Prof. Mosharaf Chowdhury} \hfill 2021 - 2022
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Created a platform capable of simulating the behavior of millions of user devices, thereby allowing FL developers to evaluate the performance of their FL applications.

\item Collected and formatted the largest benchmarking dataset for various FL tasks, focusing on various challenges like data heterogeneity, device heterogeneity, and connectivity conditions.

\end{itemize}

\noindent  
\textbf{High-dimensional Data Index: Adaptive Product Quantization Supporting Data Streaming} \\
\textit{Advisor: Prof. Samuel Madden, MIT} \hfill May 2019 - Jan 2020 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Proposed an ANN (appropriate nearest neighbor) search model based on product quantization (PQ) to support fast ANN searches in high dimensional scalable dynamic databases with high query speed and high accuracy simultaneously.
%\item Implemented the proposed algorithm and state-of-the-art algorithms (LSH, HNSW, PQ) for ANN search tasks, with experiment results showing that our proposed model is 2 - 3.6 times faster than the baseline, while keeping high accuracy.
\end{itemize}  
% \\
% \textbf{Machine Learning Based Route Recommendation System} \\
% \textit{Advisor: Prof. Siqian Shen, Umich. Sponsored by Didi Chuxing
% }
% \hfill Feb 2019 - May 2019, May 2020 - Aug 2020

% \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
% \item  Investigated machine learning and robust optimization to build a route recommendation system for ride-sharing.

% %\item  Investigated machine learning and robust optimization to build a route recommendation system to predict a customized route choice for ride-sharing.
% % \item Proposed Mean-Field reinforcement learning with grid-based simulator to do order dispatching and driver repositioning under large environment dynamics. 
% \end{itemize}  
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{COMPUTER SKILLS}} \\
\noindent \textbf{Skill:} 
C++, Python, Rust, SQL, Java, Matlab, C, HTML

\end{document}



